### 2019-05-22 paper/1.tex
1

\documentclass{llncs}
\usepackage{graphicx}
\usepackage{geometry}
\geometry{margin=2cm}
\usepackage{mathtools}
\usepackage{listings}

\begin{document}
\title{Contribution Title\thanks{Supported by organization x.}}
\author{Xi, Du\inst{1}}
\institute{Australian National University, Australia}
\maketitle 
\begin{abstract}
While the recent surge of neural networks in the name of deep learning literally suggests larger and larger networks, 
small networks have also received growing attention lately. 
So has the technique to make a trained network smaller while keeping its inference ability,
which is called network pruning or network reduction. 
In this work, I briefly review some of the network reduction techniques and 
experiment with one of the early methods \cite{method} using 
a data set about human eye movement during reading \cite{data}

\keywords{Neural network, Deep learning, 
Small data, Interpretability, Network pruning, Network reduction.}
\end{abstract}

\section{Introduction}

Deep as in deep learning,
the word leading the current resurgence of neural networks in machine learning 
and artificial intelligence,
intrinsically means larger-than-before neural networks with more and more layers and,
frequently but not necessarily,
more neurons in each layer.
However,
larger networks not only consume more computational resource during training and inference,
but are also harder to understand,
analyze and debug when problems arise.
Most importantly,
overly complex networks usually lead to bad generalisation power.
So given similar predictive power,
it is desirable to use a smaller network whenever possible.
In addition,
although neural networks are said to be bad at this in general,
smaller networks are still better in terms of interpretability,
an emerging topic in machine learning \cite{interp}.

\section{Literature Review}

The first significant work to bring the size of a trained neural network 
down was probably \cite{prune0},
where the word ¿pruning¿ was used and started being the most widely used terminology
for making a trained neural network smaller. 
However, a drawback of this word is its connotations of simply removing neurons 
without changing the remaining ones, 
which is less interesting than changing weights of neurons so that they work equivalently 
to a larger network. 
This was probably the reason the method we based on was named network reduction \cite{method}.

\section{Method}

\subsection{Preliminary}

First of all, my implementation and experimental setup 
are concerned about a 3-layer network of a single 
hidden layer of $H$ neurons. In the following discussion 
$N$ stands for the number of entries in the training set.

\subsection{Implementation of the Network Reduction Technique}

The network reduction paper \cite{method} mentioned many ways in which 
networks can be pruned. 
However, only two ways were discussed in detail. 
The first was considering whether a group of hidden layer units 
can be removed or compressed into one. 
Unfortunately, a straightforward implementation would require examining each 
power set of hidden units, to the complexity of $O(2^H)$. 
This is not feasible for any practically-sized neural network, 
so I focused on the second technique, {\em Distinctiveness}.

The {\em Distinctiveness} method examines each pair of hidden units, 
and then combine them into one when they are similar enough in terms of 
outputs of the training set, resulting in $O(H^2)$ tests, 
which is much more manageable. 
While there may be groups of three or more hidden units that can be collapsed into one, 
they are already catered by the $O(n^2)$ tests. 
For example, if hidden unit A and hidden unit B were deemed similar 
enough to be combined into one, 
and then hidden unit A and hidden unit C were deemed similar enough as well, 
my implementation would remove B at first, then remove C, 
adding weights to A accordingly.

The similarity between hidden units are established by comparing the angles 
between the vectors of hidden unit outputs. 
More specifically, a vector of the output of the hidden unit $A$, 
is just the outputs of $A$ across training data point. 
In my implementation, 
these $N$-dimension vectors are computed all together at once into an $N\times H$ matrix, 
avoiding an explicit loop. 
Pythonic loops in PyTorch are extremely expensive and should be avoided whenever possible.
While the original paper listed actual values of vector angles, 
there is no real need to actually bother with an inverse trigonometry function. 
Only the cosine is necessary, since I can threshold on the cosine value directly, 
which is
\begin{equation}
\cos(\theta) = \frac{\vec{a}\cdot \vec{b} }{\lVert \vec{a}\rVert \lVert \vec{b}\rVert }
\end{equation}
where $\vec{a}$ and $\vec{b}$ are $N$-dimensional vectors.
Because there are $H$ such vectors,
we can consider the $H$ $N$-dimensional vectors together
as one $H\times N$ matrix $h^T$,
where its $N\times H$ transpose $h$ happens to be
a natural occurence when training
neural network with PyTorch.
Then the $H^2$ dot products are computed with one $H\times N$ matrix
\begin{equation}
	P=h^Th~.
\end{equation}
The matrix $L$ of $H^2$ numerators can be computed in a similar fashion with
matrix operations instead of explicit loops.
Finally an $H\times H$ matrix $C$ of cosine values are computed 
by an element-wise divison of $P$ over $L$.
Note that $P$, $L$ and $C$ are all $H\times H$ symmetric matrices.
While the the cosines between different points are computed twice this way, 
it is still far more efficient than an explicit pythonic loop.

Now that I have the matrix of cosines, I have to run an explicit loop
to prune the hidden units.
However, the pruning happens only after many cycles of training,
so the cost is not a major issue compared to that of training.
For each pair of hidden units $i$ and $j$ ($0<i<j<=H$ and $i,j$ actually stands
for indices of hidden units), 
when the absolute value of the cosine of their angle, that is $|C_{i,j}|$, is greater
than a certain threshold $c$ where $0<=c<=1$, 
the $j$th hidden unit is removed.
In practice, I simply set its weight into the output layer to zero.
The weight is multipled by the cosine value $C_{i,j}$ 
and added to the out-going weight of $i$th hidden unit.
Of course, in theory either $i$ or $j$ can be kept,
but there is no obvious way to prefer one. 
Randomisation is not necessary either, because the
order of hidden units is already random in a sense.
Multiplication by $C_{i,j}$ automatically takes care
of the sign of the $C_{i,j}$. It may also be
argued that multiplication by $C_{i,j}$ is 
preferrable than simple addition and subtraction
because the angle is not strictly $0^\circ$ or $180^\circ$.
But I am already assuming that $|C_{i,j}|\simeq 1$, so it does not really matter.

An additional condition for the pruning is that hidden unit $i$
has not already been pruned, that is, its outgoing weight is not strictly zero.
This is an exact floating point equality comparison
arguably against common coding practice.
The rationale is that I am using the exact zero as the flag for having been pruned.
Even if a node happens to have zero outgoing weight immediately after training,
I lose no accuracy by treating it as having been pruned.
On the other hand, if I set the outgoing weight of hidden unit $j$ to zero
and move the weight, I fail to actually reduce the number of hidden units.

\subsection{Implementation of Neural Network}

The neural network was implemented with PyTorch.
Since the network is simple, I used 
straightforward matrix (or tensor in PyTorch jargon) computations and autograd
with very little content from \verb|torch.nn|.

\subsubsection{Training}

In the training phase,
The input is treated as an $N\times D_{in}$ matrix $X$.
$D_{in}$ is the dimensionality of the data, effectively $4$ for 
the eye-gaze dataset \cite{data}.
Weights from the input layer to the hidden layer is stored 
in an $D_{in} \times H$ matrix $W_1$.
Then obviously $XW_1$ becomes the inputs of activation functions.
The activation functions are the same for the $H$ hidden units.
However, I have made the activation function configurable in the program,
enabling comparison of networks with different activation functions.
The dimensionality of output, $D_{out}$ is 1 because this is a
classification test.
The weights from the hidden layer to the output layer form a 
$H \times D_{out}$ matrix $W_2$.
The outputs of the training set are
an $H \times D_{out}$ matrix $Y$
while the predicted outputs are $Y_{pred}$ of the same dimension.
The prediction is computed by
\begin{equation}
Y_{pred} = hW_2~.
\end{equation}
Finally the back-propogation is handled by standard PyTorch
autograd facility.

\subsubsection{Testing}

The testing phase is handled by exactly the same matrix operations
of the training phase,
albeit the dimensions of input and output matrices have $N'$ rows instead of $N$ rows,
where $N'$ is the size of the test set.
The autograd facility of PyTorch needs to be temporarily disabled with
\verb|torch.no_grad()| when executing the testing phase.

\subsection{Experiments}

\section{First Section}
\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.

Subsequent paragraphs, however, are indented.

\subsubsection{Sample Heading (Third Level)} Only two levels of
headings should be numbered. Lower level headings remain unnumbered;
they are formatted as run-in headings.

\paragraph{Sample Heading (Fourth Level)}
The contribution should contain no more than four levels of
headings. Table~\ref{tab1} gives a summary of all heading levels.

\begin{table}
\caption{Table captions should be placed above the
tables.}\label{tab1}
\begin{tabular}{|l|l|l|}
\hline
Heading level &  Example & Font size and style\\
\hline
Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
\hline
\end{tabular}
\end{table}

\noindent Displayed equations are centered and set on a separate
line.
\begin{equation}
x + y = z
\end{equation}
Please try to avoid rasterized images for line-art diagrams and
schemas. Whenever possible, use vector graphics instead (see
Fig.~\ref{fig1}).

\begin{theorem}
This is a sample theorem. The run-in heading is set in bold, while
the following text appears in italics. Definitions, lemmas,
propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
Proofs, examples, and remarks have the initial word in italics,
while the following text appears in normal font.
\end{proof}
For citations of references, we prefer the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
and a homepage~\cite{ref_url1}. Multiple citations are grouped
\cite{ref_article1,ref_lncs1,ref_book1},
\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
\bibitem{ref_article1}
Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

\bibitem{ref_lncs1}
Author, F., Author, S.: Title of a proceedings paper. In: Editor,
F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
Springer, Heidelberg (2016).

\bibitem{ref_book1}
Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
Location (1999)

\bibitem{ref_proc1}
Author, A.-B.: Contribution title. In: 9th International Proceedings
on Proceedings, pp. 1--2. Publisher, Location (2010)

\bibitem{ref_url1}
LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
Oct 2017
\end{thebibliography}
\end{document}

### 2019-05-22 paper/paper.tex
1

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
\usepackage{amsmath,amssymb} % define this before the line numbering.
%\usepackage{ruler}
\usepackage{color}

%\documentclass{llncs}
%\usepackage{graphicx}
%\usepackage{geometry}
%\geometry{margin=2cm}
%\usepackage{amsmath}

\usepackage{pgfplots}
\usepackage{filecontents}
\usepackage[caption=false]{subfig}
\usepackage{listings}
\lstset{
basicstyle=\small\ttfamily,
columns=flexible,
breaklines=true
}

\begin{document}
\title{Evaluating Network Reduction Techniques with Eye Gaze Data}
\author{Xi Du}
\institute{Australian National University, Australia\\
\email{u6559090@anu.edu.au}}
\maketitle 
\begin{abstract}
\cite{method}

\keywords{Neural network, Deep learning, 
Small data, Interpretability, Network pruning, Network reduction.}
\end{abstract}

\section{Introduction}

\section{Literature Review}

\section{Method}

\subsection{Preliminary}

\subsection{Implementation of the Network Reduction Technique}

\subsection{Implementation of Neural Network}

\subsubsection{Training Phase}

\subsubsection{Testing Phase}

\subsection{Data Set}

\subsubsection {Format and Preparation}

\subsubsection {(Not Really) Time-Series}

\subsubsection {Rationale}

\subsection{Hyperparameters and Experiments}

\subsubsection{Activation Function}

\subsubsection{Learning Rate}

\subsubsection{Hidden Layer Size}

\subsection{Evaluating Prediction}

\subsubsection{Binarisation and Choice of Loss}

\subsubsection{Amount of Network Reduction}

\subsubsection{Mechanism}

\subsubsection{Execution}

The program was developed under and are compatible with:
\begin{itemize}
\item Python 3.6
\item PyTorch 1.0.1.post2
\item CentOS 7 x86\_64
\end{itemize}
To run the code, execute shell commands like
\begin{verbatim}
python36 0.py 5000
\end{verbatim}
where 5000 is the number of desired training cycles to reach.
The different hyperparameters will be automatically covered.
The program automatically picks up stored models.
To start fresh, clear the stored models and outputs by
\begin{verbatim}
rm out/*/*.*
\end{verbatim}
but do not remove the directories.

\section{Results and Discussion}

\section{Conclusion and Future Work}

\begin{thebibliography}{8}
\bibitem{data}
Zhu, D., Mendis, B.S., Gedeon, T.D., Asthana, A., \& Göcke, R. (2008). A Hybrid Fuzzy Approach for Human Eye Gaze Pattern Recognition. ICONIP.
\bibitem{method}
Gedeon, T.D. and Harris, D. (1991) "Network Reduction Techniques," Proceedings International Conference on Neural Networks Methodologies and Applications, AMSE, San Diego, vol. 1: 119-126. 
\bibitem{prune0}
Penington, Jocelyn \& Dow, R.J.F.. (1988). Neural net pruning—Why and how. Proceedings of the IEEE Conference on Neural Networks. 1. 325 - 333 vol.1. 10.1109/ICNN.1988.23864. 
\bibitem{interp}
Doshi-Velez, F., \& Kim, B. (2017). Towards A Rigorous Science of Interpretable Machine Learning.
\bibitem{example_prune}
Han, S., Mao, H., \& Dally, W.J. (2016). Deep Compression: Compressing Deep Neural Network with Pruning, Trained Quantization and Huffman Coding. CoRR, abs/1510.00149.
\bibitem{example_simplification}
Sun, X., Ren, X., Ma, S., Wei, B., Li, W., \& Wang, H. (2018). Training Simplification and Model Simplification for Deep Learning: A Minimal Effort Back Propagation Method. CoRR, abs/1711.06528.
\bibitem{example_compression}
Cheng, Yu \& Wang, Duo \& Zhou, Pan \& Zhang, Tao. (2017). A Survey of Model Compression and Acceleration for Deep Neural Networks. 
\bibitem{pytorch}
Paszke, A., Gross, S., Chintala, S., Chanan, G., Yang, E., DeVito, Z., Lin, Z., Desmaison, A., Antiga, L., \& Lerer, A. (2017). Automatic differentiation in PyTorch.
\end{thebibliography}
\end{document}

### 2019-05-22 src/program.py

@@ -1,0 +1,302 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+# In[1]:
+
+
+import numpy as np
+import os
+import sys
+import scipy.io
+import scipy.misc
+import imageio
+import tensorflow as tf
+import matplotlib.pyplot as plt
+from matplotlib.pyplot import imshow
+from PIL import Image
+from IPython.display import Image, display
+
+
+# In[2]:
+
+
+class Configuration:
+    COLOR_CHANNEL = 3
+    CONTENT_IMAGE = 'images/content_image.jpg'
+    IMAGE_HEIGHT= imageio.imread(CONTENT_IMAGE).shape[0]
+    IMAGE_WIDTH= imageio.imread(CONTENT_IMAGE).shape[1]
+    STYLE_IMAGE = 'images/style_image.jpg'
+    OUPUT = 'images/'
+    NOISE_RATIO = 0.6
+    ALPHA = 100
+    BETA = 5
+    PATH_VGG_MODEL = 'pretrained_model/imagenet-vgg-verydeep-19.mat'
+    MEAN = np.array([123.68,116.779, 103.939]).reshape((1,1,1,3))
+
+
+# In[3]:
+
+
+def load_vgg(path_location):
+    vgg = scipy.io.loadmat(path_location)
+    vgg_layers = vgg['layers']
+    
+    def _weights(layer,expected_layer_name):
+        weight_basis = vgg_layers[0][layer][0][0][2]
+        weights = weight_basis[0][0]
+        basises = weight_basis[0][1]
+        layer_name = vgg_layers[0][layer][0][0][0][0]
+        return weights,basises
+    
+    def _relu(conv_layer):
+        return tf.nn.relu(conv_layer)
+    
+    def _conv(previous_layer,layer,layer_name):
+        wght,bsis = _weights(layer,layer_name)
+        wght = tf.constant(wght)
+        bsis_reshape = np.reshape(bsis,(bsis.size))  
+        bsis = tf.constant(bsis_reshape)
+        return tf.nn.conv2d(previous_layer,filter=wght,strides=[1,1,1,1],padding='SAME')+ bsis
+    
+    def _conv_relu(previous_layer,layer,layer_name):
+        return _relu(_conv(previous_layer,layer,layer_name))
+    
+    def _average_pooling(previous_layer):
+        return tf.nn.avg_pool(previous_layer,ksize=[1,2,2,1],strides=[1,2,2,1],padding='SAME')
+    
[…]

### 2019-05-24 paper/paper.tex
1

@@
 \begin{document}
-\title{Evaluating Network Reduction Techniques with Eye Gaze Data}
+\title{Neural Network Transfer extended with Multiple Style Images}
 \author{Xi Du}
@@
 
-\subsection{Implementation of the Network Reduction Technique}
-
 \subsection{Implementation of Neural Network}
-
-\subsubsection{Training Phase}
+Since we are not training the neural network, 
+the model is just a sequence of functions on arrays.
 
@@
 
-\subsubsection{Activation Function}
+For the vanilla style-transfer algorithm, there were a few hyper-parameters that 
+affected the result.
+\begin{itemize}
+\item Number of iterations in the optimization. 
+We did not have to expriment with different numbers of iterations though.
+It was more sensible to run the algorithm for more-than-enough iterations and store the intermediate results.
+\item Weights of style loss $k_S$ and content loss $k_C$ in the optimisation target. 
+Although these appeared to be two parameters,
+actually only their ratio $k_S/k_C$ mattered.
+We simply fixed $k_C=1$ and varied $k_S$.
+\item Choice of initial values. Some sensible choices were:
+\begin{itemize}
+\item White noise.
+\item White.
+\item Black.
+\item The model mean.
+\item The content image.
+\item The style image.
+\item The average of the content image and the style image.
+\end{itemize}
+\end{itemize}
+
+%\subsubsection{Activation Function}
 
@@
 \begin{thebibliography}{8}
-\bibitem{data}
-Zhu, D., Mendis, B.S., Gedeon, T.D., Asthana, A., \& Göcke, R. (2008). A Hybrid Fuzzy Approach for Human Eye Gaze Pattern Recognition. ICONIP.
+\bibitem{nst}
+Gatys, L., Ecker, A., \& Bethge, M. (2016). A neural algorithm of artistic style. Journal of Vision, 16(12), 326. doi:10.1167/16.12.326
 \bibitem{method}

### 2019-05-25 rollback/neural_style_tutorial.py
1

@@ -1,0 +1,399 @@
+"""
+Neural Transfer Using PyTorch
+=============================
+
+
+**Author**: `Alexis Jacq <https://alexis-jacq.github.io>`_
+ 
+**Edited by**: `Winston Herring <https://github.com/winston6>`_
+
+Introduction
+------------
+
+This tutorial explains how to implement the `Neural-Style algorithm <https://arxiv.org/abs/1508.06576>`__
+developed by Leon A. Gatys, Alexander S. Ecker and Matthias Bethge.
+Neural-Style, or Neural-Transfer, allows you to take an image and
+reproduce it with a new artistic style. The algorithm takes three images,
+an input image, a content-image, and a style-image, and changes the input 
+to resemble the content of the content-image and the artistic style of the style-image.
+
+ 
+.. figure:: /_static/img/neural-style/neuralstyle.png
+   :alt: content1
+"""
+
+######################################################################
+# Underlying Principle
+# --------------------
+# 
+# The principle is simple: we define two distances, one for the content
+# (:math:`D_C`) and one for the style (:math:`D_S`). :math:`D_C` measures how different the content
+# is between two images while :math:`D_S` measures how different the style is
+# between two images. Then, we take a third image, the input, and
+# transform it to minimize both its content-distance with the
+# content-image and its style-distance with the style-image. Now we can
+# import the necessary packages and begin the neural transfer.
+# 
+# Importing Packages and Selecting a Device
+# -----------------------------------------
+# Below is a  list of the packages needed to implement the neural transfer.
+#
+# -  ``torch``, ``torch.nn``, ``numpy`` (indispensables packages for
+#	neural networks with PyTorch)
+# -  ``torch.optim`` (efficient gradient descents)
+# -  ``PIL``, ``PIL.Image``, ``matplotlib.pyplot`` (load and display
+#	images)
+# -  ``torchvision.transforms`` (transform PIL images into tensors)
+# -  ``torchvision.models`` (train or load pre-trained models)
+# -  ``copy`` (to deep copy the models; system package)
+
+from __future__ import print_function
+
+import torch
+import torch.nn as nn
+import torch.nn.functional as F
+import torch.optim as optim
+
+from PIL import Image
+import matplotlib.pyplot as plt
+
+import torchvision.transforms as transforms
+import torchvision.models as models
+
+import copy
+
+
[…]

### 2019-05-25 src/program.py

@@ -1,9 +1,6 @@
 #!/usr/bin/env python
 # coding: utf-8
 
-# In[1]:
-
-
 import numpy as np
 import os
 import sys
@@ -15,10 +12,6 @@ import matplotlib.pyplot as plt
 from matplotlib.pyplot import imshow
 from PIL import Image
 from IPython.display import Image, display
-
-
-# In[2]:
-
 
 class Configuration:
     COLOR_CHANNEL = 3
@@ -32,10 +25,6 @@ class Configuration:
     BETA = 5
     PATH_VGG_MODEL = 'pretrained_model/imagenet-vgg-verydeep-19.mat'
     MEAN = np.array([123.68,116.779, 103.939]).reshape((1,1,1,3))
-
-
-# In[3]:
-
 
 def load_vgg(path_location):
     vgg = scipy.io.loadmat(path_location)
@@ -91,46 +80,25 @@ def load_vgg(path_location):
     
     return graph
 
-
-# In[4]:
-
-
 def _generate_white_noise_content_image(content_image):
     white_noise_image = np.random.uniform(-20,20,(1,Configuration.IMAGE_HEIGHT,Configuration.IMAGE_WIDTH,Configuration.COLOR_CHANNEL)).astype('float32')
     input_content_image = white_noise_image + content_image
     return input_content_image
-
-
-# In[5]:
-
 
 def _reshape_normalize(img):
     img = np.reshape(img,((1,) + img.shape))
     img = img - Configuration.MEAN
     return img
 
-
-# In[6]:
-
-
 def _save_image(path_location,output_image):
     output_image = output_image.astype('float32') + Configuration.MEAN
     output_image = np.clip(output_image[0],0,255).astype('uint8')
     imageio.imwrite(path_location,output_image)
 
-
-# In[7]:
-
-
 input_c_image = imageio.imread(Configuration.CONTENT_IMAGE)
 input_content_image = _reshape_normalize(input_c_image)
 input_s_image = imageio.imread(Configuration.STYLE_IMAGE)
 input_style_image = _reshape_normalize(input_s_image)
-
-
-
-# In[8]:
-
 
 def _compute_content_loss(activation_content_image, activation_generate_image):
     m, N,M1,M2 = activation_generate_image.get_shape().as_list()
@@ -140,16 +108,8 @@ def _compute_content_loss(activation_content_image, activation_generate_image):
[…]

### 2019-05-26 paper/paper.tex
1

@@
 \begin{document}
-\title{Neural Network Transfer extended with Multiple Style Images}
+\title{Dissecting Neural Style Transfer}
 \author{Xi Du}
@@
 
-\subsection{Preliminary}
+\subsection{Deep Neural Network}
+
+For the purpose of implementing and even extending neural style transfer algorithms,
+it is not necessary to understand how a neural network is trained, because
+we can use pretrained model for example vgg19 \cite{vgg19}.
+
+It is necessary to point out that a deep neural network that neural style transfer
+is concerend about
+is just a sequence of functions
+$F_1,F_2,F_3,...$
+whose inputs and outputs are all multi-dimensional arrays, as illustrated in Figure \ref{f1f2f3}.
+\begin{figure}
+\center
+\includegraphics[width=0.6\textwidth]{f1f2f3.pdf}
+\caption{A deep neural network \label{f1f2f3}}
+\end{figure}
+Because the arrays have usually more than two numbers of dimensions
+they are not really matrices.
+The arrays are called tensors (as in TensorFlow or torch.Tensor in PyTorch) 
+but actual tensor algebra in a mathematical sense is rarely relevant.
+The functions need to be differentiable, which is handled automatically by modern 
+deep learning frameworks.
+Other than that we can treat the functions as blackboxes because we are 
+not concerned of training the model.
+
+For the vgg19 model that most neural style transfer implementations available are based on,
+The inputs and outpus of each layer are all arrays with 4 dimensions.
+The word ``dimension'' here may mean something slightly different from what ``dimension'' means in
+for example ``$3$-dimension vector''. 
+Some people call the number of dimensions ``rank'' which would then raise another confusion with the rank of matrices.
+
+The 1st dimension is the ``batch'' dimension, which means that you can put several images through the
+series of functions.
+In neural style transfer implementations it is usually just one image each time.
+So the 1st dimension is always 1, even between the $F$ functions, throughout this work.
+
+The 2nd dimension is the ``feature'' dimension. For a raw RGB image, it is 3.
+Intermediate values between, for example, $F_3$ and $F_4$, usually 
+have a size much larger than 3, such as 64 or 128
+
+\subsection{Vanilla neural style transfer}
 

### 2019-05-26 paper/paper.tex
1

@@
 \keywords{Neural network, Deep learning, 
-Small data, Interpretability, Network pruning, Network reduction.}
+Small data, Interpretability .}
 \end{abstract}
@@
 not concerned of training the model.
+A ``layer'' in a deep neural network refers to a few consecutive functions together.
+It is not particularly necessary to consider ``layers'' in this work. 
+Though it is important to note that in our illustrations there are functions instead of layers.
 
+\subsection{vgg19 model}
 For the vgg19 model that most neural style transfer implementations available are based on,
@@
 Some people call the number of dimensions ``rank'' which would then raise another confusion with the rank of matrices.
+We give an illustration for the vgg19 model in Figure \ref{vgg512}
+\begin{figure}
+\center
+\includegraphics[width=\textwidth]{vgg512.pdf}
+\caption{The VGG19 model with an $512\times512$ RGB image as its input \label{vgg512}}
+\end{figure}
 
@@
 The 2nd dimension is the ``feature'' dimension. For a raw RGB image, it is 3.
-Intermediate values between, for example, $F_3$ and $F_4$, usually 
-have a size much larger than 3, such as 64 or 128
+Intermediate arrays between, for example, $F_3$ and $F_4$, usually 
+have a size much larger than 3, such as 64 or 128.
+
+The 3nd and 4th dimensions are just spatial locations. 
+For a $512\times512$ image they are 512 and 512. 
+For intermediate arrays, these 2 dimensions are sometimes scaled down
+to half or even $\frac{1}{4}$ of the sizes of the image.
+
+The functions $F_1,F_2,F_3,...$ now have meaningful names such as relu\_1, conv\_2 now.
+[Not actually necessary to know but insert your elaborations here]
+
+The arrays after the initial image are called feature maps, because their value means
+``how much a feature x exists at position y and x''.
+For example in a $1\times64\times512\times512$ feature map, it means there are 64 types of features.
+and its [1, 17, 111, 222] element, would then mean the extent that the 17th type feature exists
+at the 111 row and 222 column position of the image.
 

### 2019-05-26 paper/paper.tex
1
experiments

@@
 \usepackage{amsmath,amssymb} % define this before the line numbering.
+
+\DeclareMathOperator*{\argmin}{argmin}
+
 %\usepackage{ruler}
@@
 For example in a $1\times64\times512\times512$ feature map, it means there are 64 types of features.
-and its [1, 17, 111, 222] element, would then mean the extent that the 17th type feature exists
-at the 111 row and 222 column position of the image.
+and its [1, 17, 111, 222] element, would then refer to the extent that the 17th type feature exists
+at the position of the 222th column of the 111th row. This ``extent'' could also be negative.
 
@@
 
-\subsection{Implementation of Neural Network}
-Since we are not training the neural network, 
-the model is just a sequence of functions on arrays.
+The vanillay neural style transfer algorithm \cite{nst} is 
+structured as iteratively solving an optimisation problem.
+The argument to optimise is the image as a multidimensional array,
+of size $1\times3\times512\times512$ for example.
+The interative solver can be many, but in our case it is 
+L-BFGS [Maybe elaborate on L-BFGS here]. 
+The initial value of the argument could be either white noise or the content image,
+but the latter appeared to make the optimisation much easier.
 
-\subsubsection{Testing Phase}
+The key issue here is still how to structure the optimisation target.
+The value to minimise is a linear combination of a ``style loss'' 
+and ``content loss''.
+Although these appeared to be two weights,
+actually only their ratio mattered.
+We simply fixed the weight of the content loss to 1 and
+leave the weight of the style loss as a adjustable hyperparameter $k$.
+\begin{align}
+\argmin\limits_{\text{image}} (kL_\text{style}+L_\text{content})
+\end{align}
+
+The content loss is the easier one of the two losses.
 
@@
 It was more sensible to run the algorithm for more-than-enough iterations and store the intermediate results.
-\item Weights of style loss $k_S$ and content loss $k_C$ in the optimisation target. 
-Although these appeared to be two parameters,
-actually only their ratio $k_S/k_C$ mattered.
-We simply fixed $k_C=1$ and varied $k_S$.
 \item Choice of initial values. Some sensible choices were:

### 2019-05-26 rollback/neural_style_tutorial.py

@@ -96,7 +96,12 @@ device = torch.device("cuda" if torch.cuda.is_available() else "cpu")
 #	 with name ``images`` in your current working directory.
 
 # desired size of the output image
-imsize = 512 if torch.cuda.is_available() else 128  # use small size if no gpu
+#imsize = 512 if torch.cuda.is_available() else 128  # use small size if no gpu
+#imsize = 256
+#imsize = 128
+#imsize = 32
+#imsize = 128
+imsize = 512
 
 loader = transforms.Compose([
 	transforms.Resize(imsize),  # scale imported image
@@ -110,11 +115,7 @@ def image_loader(image_name):
 	return image.to(device, torch.float)
 
 
-style_img = image_loader("./picasso.jpg")
-content_img = image_loader("./dancing.jpg")
 
-assert style_img.size() == content_img.size(), \
-	"we need to import style and content images of the same size"
 
 
 ######################################################################
@@ -160,6 +161,7 @@ def gram_matrix(input):
 	# (c,d)=dimensions of a f. map (N=c*d)
 
 	features = input.view(a * b, c * d)  # resise F_XL into \hat F_XL
+	#print(features.shape)
 
 	G = torch.mm(features, features.t())  # compute the gram product
 
@@ -168,18 +170,131 @@ def gram_matrix(input):
 	return G.div(a * b * c * d)
 	#return G
 
+def gram_matrix_no_norm(input):
+	a, b, c, d = input.size()
+	features = input.view(a * b, c * d)
+	return torch.mm(features, features.t())
+
+
+#def gram_t(x):
+#	print(x.shape)
+#	return gram_matrix(x.transpose(2,3))
+
+def dislocate1(arr):
+	return arr.sum(dim=(2,3))/arr.shape.numel()
+
+def dislocate2(arr):
+	return (arr**2).sum(dim=(2,3))/arr.shape.numel()
+
+#def dislocate4(arr):
+#	return (arr**4).sum(dim=(2,3))/arr.shape.numel()
+
+def dislocate3(arr):
+	return arr.abs().sum(dim=(2,3))/arr.shape.numel()
+
+def dislocate4(arr):
+	a, b, c, d = arr.size()
+	features = arr.view(a*b,c*d)
+	return features[:,None,:] @ features[:,:,None] / (a*b*c*d)
+
+#def dislocate5(arr):
+#	return (arr**2).flatten(start_dim=2).sort(dim=2)[0]/arr.shape.numel()
+
+#def dislocate5(arr):
[…]

### 2019-05-26 paper/paper.tex
1

@@
 For the vgg19 model that most neural style transfer implementations available are based on,
-The inputs and outpus of each layer are all arrays with 4 dimensions.
+The inputs and outpus of each function are all arrays with 4 dimensions.
 The word ``dimension'' here may mean something slightly different from what ``dimension'' means in
@@
 
-The content loss is the easier one of the two losses.
+The content loss is the easier one to explain of the two losses.
+It is the mean square error between the outputs of a certain function in the
+vgg19 taking the current argument image and the content image as inputs respectively.
+We say ``a certain'' function because the output of which function to choose is
+adjustable.
+A typical choice is the output of \verb|conv_4| function. See Figure \ref{contentloss}.
+\begin{figure}
+\center
+\includegraphics[width=\textwidth]{contentloss.pdf}
+\caption{The content loss \label{contentloss}}
+\end{figure}
 

### 2019-05-26 rollback/neural_style_tutorial.py

@@ -410,7 +410,7 @@ def get_style_model_and_losses(dislocator, cnn, normalization_mean, normalizatio
 		else:
 			raise RuntimeError('Unrecognized layer: {}'.format(layer.__class__.__name__))
 
-		model.add_module('printSize before '+name, PrintSize('before '+name))
+		#model.add_module('printSize before '+name, PrintSize('before '+name))
 		model.add_module(name, layer)
 
 		if name in content_layers:
@@ -535,19 +535,20 @@ if False:
 (fname,f) = usableDislocators[0]
 for content_name in ['dancing']:
 	for style_name in ['picasso']:
-		for (cl,sl) in [(['conv_4'],['conv_1', 'conv_2', 'conv_3', 'conv_4', 'conv_5']),
-			(['conv_4','conv_5']),
-			(['conv_4','conv_4']),
-			(['conv_1','conv_1']),
-			(['relu_1','relu_1']),
-			(['conv_2','conv_2'])]:
+		for (cl,sl) in [
+			(['conv_4'],['conv_1', 'conv_2', 'conv_3', 'conv_4', 'conv_5']),
+			(['conv_4'],['conv_5']),
+			(['conv_4'],['conv_4']),
+			(['conv_1'],['conv_1']),
+			(['relu_1'],['relu_1']),
+			(['conv_2'],['conv_2'])]:
 			content_img = image_loader("./"+content_name+".jpg")
 			style_img = image_loader("./"+style_name+".jpg")
 			assert style_img.size() == content_img.size(), \
 				"we need to import style and content images of the same size"
 			input_img = content_img.clone()
 			output = run_style_transfer(content_name+'-'+ style_name+'-'+str(imsize)+'-'+fname
-										+','.join(cl)+'-'+','.join(sl), 
+										+'-'+','.join(cl)+'-'+','.join(sl), 
 										f, 
 										cl, sl,
 										cnn, cnn_normalization_mean, cnn_normalization_std,

### 2019-05-26 paper/paper.tex
1

@@
 The functions $F_1,F_2,F_3,...$ now have meaningful names such as relu\_1, conv\_2 now.
-[Not actually necessary to know but insert your elaborations here]
+[[[[Not actually necessary to know but insert your elaborations here]]]]
 
@@
 The interative solver can be many, but in our case it is 
-L-BFGS [Maybe elaborate on L-BFGS here]. 
+L-BFGS [[[[Maybe elaborate on L-BFGS here]]]]. 
 The initial value of the argument could be either white noise or the content image,
@@
 
-The content loss is the easier one to explain of the two losses.
+The content loss $L_\text{content}$ is the easier one to explain of the two losses.
 It is the mean square error between the outputs of a certain function in the
@@
 \includegraphics[width=\textwidth]{contentloss.pdf}
-\caption{The content loss \label{contentloss}}
+\caption{The content loss $L_{content}$ \label{contentloss}}
 \end{figure}
 
-\subsection{Data Set}
+The style loss $L_\text{content}$ can actually be a sum of several style losses, or sometimes just one.
+For each style loss, 
+both the current image under optimisation and the style image are passed through the vgg19 model.
+The two outputs of a certain function in the model are extracted, 
+and converted to Gram matrices. We will elabrate on what Gram matrices are,
+for now they are just square matrices computed from multidimensional arrays (i.e. feature maps).
+For example, the Gram matrix (in the style transfer algorithm) of a $1\times64\times512\times512$ array
+is a $64\times64$ matrix.
+The point is to compute something that describe the distributions of features
+in the image without the spatial information of where the features are.
+Gram matrices describe the distributions with correlation between features.
+The several style losses are computed with the outputs of different functions.
+Otherwise, each of the several style losses are computed in exactly the same way.
 
-\subsubsection {Format and Preparation}
+Again outputs of which functions in the model to derive style losses from is really adjustable.
+A nice default is \verb|conv_1|,\verb|conv_2|,...,\verb|conv_5|. We illustrate
+the style losses derived \verb|conv_1| and \verb|conv_4| in Figure $\ref{stylelosses}$.
 
-\subsubsection {(Not Really) Time-Series}
+\begin{figure}
+\center
+\includegraphics[width=\textwidth]{stylelosses}
+\end{figure}
 
-\subsubsection {Rationale}
+\subsection{Gram matrix}
+[[[[Elaborate on gram matrix here]]]]
 
-\subsection{Hyperparameters and Experiments}
+\subsection{Removing the spatial information in other ways}
+We think that the most brilliant aspect of the neural style transfer algorithm,
+apart from the general structure, is the use of Gram matrices to compare 
+distributions of features in two images, so that where the features are does not matter.
+It gives really nice insight on what ``artistic style'' means.
 
-For the vanilla style-transfer algorithm, there were a few hyper-parameters that 
-affected the result.
-\begin{itemize}
-\item Number of iterations in the optimization. 
-We did not have to expriment with different numbers of iterations though.
-It was more sensible to run the algorithm for more-than-enough iterations and store the intermediate results.
-\item Choice of initial values. Some sensible choices were:
-\begin{itemize}
-\item White noise.
-\item White.
-\item Black.
-\item The model mean.
-\item The content image.
-\item The style image.
-\item The average of the content image and the style image.
-\end{itemize}
-\end{itemize}
+However, could we achieve the same results with other
 
-%\subsubsection{Activation Function}
-
-\subsubsection{Learning Rate}
-
-\subsubsection{Hidden Layer Size}
-
-\subsection{Evaluating Prediction}
-
-\subsubsection{Binarisation and Choice of Loss}
-
-\subsubsection{Amount of Network Reduction}
-
-\subsubsection{Mechanism}
-
-\subsubsection{Execution}
-
-The program was developed under and are compatible with:
-\begin{itemize}
-\item Python 3.6
-\item PyTorch 1.0.1.post2
-\item CentOS 7 x86\_64
-\end{itemize}
-To run the code, execute shell commands like
-\begin{verbatim}
-python36 0.py 5000
-\end{verbatim}
-where 5000 is the number of desired training cycles to reach.
-The different hyperparameters will be automatically covered.
-The program automatically picks up stored models.
-To start fresh, clear the stored models and outputs by
-\begin{verbatim}
-rm out/*/*.*
-\end{verbatim}
-but do not remove the directories.
-
-\section{Results and Discussion}
+\section{Experiments and Discussion}
 

### 2019-05-26 rollback/neural_style_tutorial.py

@@ -107,7 +107,6 @@ loader = transforms.Compose([
 	transforms.Resize(imsize),  # scale imported image
 	transforms.ToTensor()])  # transform it into a torch tensor
 
-
 def image_loader(image_name):
 	image = Image.open(image_name)
 	# fake batch dimension required to fit network's input dimensions
@@ -517,43 +516,55 @@ def run_style_transfer(prefix, dislocator, content_layers, style_layers,
 if False:
 	cl = content_layers_default
 	sl = style_layers_default
-	#layer_string = ','.join(cl) + '-' + ','.join(sl)
 	for content_name in ['dancing']:
 		for style_name in ['picasso']:
 			for (fname,f) in usableDislocators:
 				content_img = image_loader("./"+content_name+".jpg")
 				style_img = image_loader("./"+style_name+".jpg")
-				assert style_img.size() == content_img.size(), \
-					"we need to import style and content images of the same size"
+				assert style_img.size() == content_img.size()
 				input_img = content_img.clone()
 				output = run_style_transfer(content_name+'-'+ style_name+'-'+str(imsize)+'-'+fname, 
 											f, 
 											cl, sl,
 											cnn, cnn_normalization_mean, cnn_normalization_std,
 											content_img, style_img, input_img)
+if False:
+	(fname,f) = usableDislocators[0]
+	for content_name in ['dancing']:
+		for style_name in ['picasso']:
+			for (cl,sl) in [
+				(['conv_4'],['conv_1', 'conv_2', 'conv_3', 'conv_4', 'conv_5']),
+				(['conv_4'],['conv_5']),
+				(['conv_4'],['conv_4']),
+				(['conv_1'],['conv_1']),
+				(['relu_1'],['relu_1']),
+				(['conv_2'],['conv_2'])]:
+				content_img = image_loader("./"+content_name+".jpg")
+				style_img = image_loader("./"+style_name+".jpg")
+				assert style_img.size() == content_img.size()
+				input_img = content_img.clone()
+				output = run_style_transfer(content_name+'-'+ style_name+'-'+str(imsize)+'-'+fname
+											+'-'+','.join(cl)+'-'+','.join(sl), 
+											f, 
+											cl, sl,
+											cnn, cnn_normalization_mean, cnn_normalization_std,
+											content_img, style_img, input_img)
 
+cl = content_layers_default
+sl = style_layers_default
 (fname,f) = usableDislocators[0]
[…]

### 2019-05-26 paper/paper.tex
1

@@
 \includegraphics[width=\textwidth]{contentloss.pdf}
-\caption{The content loss $L_{content}$ \label{contentloss}}
+\caption{The content loss \label{contentloss}}
 \end{figure}
@@
 Otherwise, each of the several style losses are computed in exactly the same way.
-
 Again outputs of which functions in the model to derive style losses from is really adjustable.
 A nice default is \verb|conv_1|,\verb|conv_2|,...,\verb|conv_5|. We illustrate
-the style losses derived \verb|conv_1| and \verb|conv_4| in Figure $\ref{stylelosses}$.
+the style losses derived from the output of \verb|conv_1| in Figure $\ref{styleloss}$.
 
@@
 \center
-\includegraphics[width=\textwidth]{stylelosses}
+\includegraphics[width=\textwidth]{styleloss.pdf}
+\caption{The style loss derived from the output of conv\_1 \label{styleloss}}
 \end{figure}
@@
 
-However, could we achieve the same results with other
+Now we wonder, could we achieve similar results with other ways to compare 
+distribution of features?
+One approach would be to consider the \emph{comparison} as a whole to find 
+substitute. 
+For us, it seemed more natural to consider substitute to the process of 
+transforming feature maps to Gram matrices itself, that is, 
+a mapping that removes the spatial information of where features are but retains
+the distribution of features like a histogram.
 
 \section{Experiments and Discussion}
+
+\subsection{Varying the dislocator function}
+
+\subsection{Varying the extraction points for losses}
+
+We will also show that other factors, such that the outputs of which functions to derive the style 
+losses from are not very essential and somewhat belongs to tuning.
 
@@
 Gatys, L., Ecker, A., \& Bethge, M. (2016). A neural algorithm of artistic style. Journal of Vision, 16(12), 326. doi:10.1167/16.12.326
-\bibitem{method}
-Gedeon, T.D. and Harris, D. (1991) "Network Reduction Techniques," Proceedings International Conference on Neural Networks Methodologies and Applications, AMSE, San Diego, vol. 1: 119-126. 
-\bibitem{prune0}
-Penington, Jocelyn \& Dow, R.J.F.. (1988). Neural net pruning—Why and how. Proceedings of the IEEE Conference on Neural Networks. 1. 325 - 333 vol.1. 10.1109/ICNN.1988.23864. 
+\bibitem{demyst}
+Li, Y., Wang, N., Liu, J., \& Hou, X. (2017). Demystifying Neural Style Transfer. IJCAI.
 \bibitem{interp}
 Doshi-Velez, F., \& Kim, B. (2017). Towards A Rigorous Science of Interpretable Machine Learning.
-\bibitem{example_prune}
-Han, S., Mao, H., \& Dally, W.J. (2016). Deep Compression: Compressing Deep Neural Network with Pruning, Trained Quantization and Huffman Coding. CoRR, abs/1510.00149.
-\bibitem{example_simplification}
-Sun, X., Ren, X., Ma, S., Wei, B., Li, W., \& Wang, H. (2018). Training Simplification and Model Simplification for Deep Learning: A Minimal Effort Back Propagation Method. CoRR, abs/1711.06528.
-\bibitem{example_compression}
-Cheng, Yu \& Wang, Duo \& Zhou, Pan \& Zhang, Tao. (2017). A Survey of Model Compression and Acceleration for Deep Neural Networks. 
 \bibitem{pytorch}

### 2019-05-26 paper/paper.tex
1

@@
 One approach would be to consider the \emph{comparison} as a whole to find 
-substitute. 
-For us, it seemed more natural to consider substitute to the process of 
-transforming feature maps to Gram matrices itself, that is, 
-a mapping that removes the spatial information of where features are but retains
-the distribution of features like a histogram.
+substitutes. 
+For example, minimising the mean square errors between two Gram matrices could be seen as 
+a special case for minimising a Maximum Mean Discrepancy, which means other Maximum Mean Discrepacies
+could be used \cite{MMD}.
+For us, it seemed more natural to consider substitutes for the process itself of 
+transforming a feature map into a Gram matrix. 
+That is, we will consider other
+mappings that remove the spatial information of where features are but retains
+the distribution of features, like a histogram.
+We will call such functions ``\emph{dislocators}'' in the remaing part of this work.
+Unfortunately, the word ``dislocate'' would give the connotation of moving something to somewhere else.
+However, the word ``locator'' means something that provides spatial information,
+so calling somthing that removes spatial information a ``dislocator'' is still plausible.
+
+Some ``dislocator'' functions we tried are
 
@@
 Gatys, L., Ecker, A., \& Bethge, M. (2016). A neural algorithm of artistic style. Journal of Vision, 16(12), 326. doi:10.1167/16.12.326
-\bibitem{demyst}
+\bibitem{MMD}
 Li, Y., Wang, N., Liu, J., \& Hou, X. (2017). Demystifying Neural Style Transfer. IJCAI.

### 2019-05-26 paper/paper.tex
1

@@
 ``how much a feature x exists at position y and x''.
-For example in a $1\times64\times512\times512$ feature map, it means there are 64 types of features.
-and its [1, 17, 111, 222] element, would then refer to the extent that the 17th type feature exists
+Take a $1\times64\times512\times512$ feature map for example. There are 64 types of features.
+Its [1, 17, 111, 222] element, would then refer to the extent that the 17th type feature exists
 at the position of the 222th column of the 111th row. This ``extent'' could also be negative.
@@
 The two outputs of a certain function in the model are extracted, 
-and converted to Gram matrices. We will elabrate on what Gram matrices are,
-for now they are just square matrices computed from multidimensional arrays (i.e. feature maps).
+and converted to Gram matrices. We will elabrate on what Gram matrices are later.
+For now a Gram matrix is just a square matrix computed from a multidimensional array (i.e. a feature map).
 For example, the Gram matrix (in the style transfer algorithm) of a $1\times64\times512\times512$ array

### 2019-05-26 paper/paper.tex
1

@@
 is a $64\times64$ matrix.
-The point is to compute something that describe the distributions of features
+The point is that a Gram matrix describes the distribution of features
 in the image without the spatial information of where the features are.
-Gram matrices describe the distributions with correlation between features.
+Gram matrices describe the distribution with correlation between features.
 The several style losses are computed with the outputs of different functions.
 Otherwise, each of the several style losses are computed in exactly the same way.
-Again outputs of which functions in the model to derive style losses from is really adjustable.
-A nice default is \verb|conv_1|,\verb|conv_2|,...,\verb|conv_5|. We illustrate
+Again, the outputs of which functions in the model to derive style losses from is really adjustable.
+A nice default we used was \verb|conv_1|,\verb|conv_2|,...,\verb|conv_5|. We illustrate
 the style losses derived from the output of \verb|conv_1| in Figure $\ref{styleloss}$.

### 2019-05-26 paper/paper.tex
1

@@
 
-The arrays after the initial image are called feature maps, because their value means
+The arrays after the initial image are called \emph{feature maps}, because their value means
 ``how much a feature x exists at position y and x''.
@@
 That is, we will consider other
-mappings that remove the spatial information of where features are but retains
+mappings that remove the spatial information or where features are in a feature map but retain
 the distribution of features, like a histogram.
+Such functions need to be differentiable as well, otherwise they would render the 
+optimisation infeasible.
+
 We will call such functions ``\emph{dislocators}'' in the remaing part of this work.
 Unfortunately, the word ``dislocate'' would give the connotation of moving something to somewhere else.
-However, the word ``locator'' means something that provides spatial information,
-so calling somthing that removes spatial information a ``dislocator'' is still plausible.
+Nevertheless, the word ``locator'' means something that provides spatial information,
+so calling somthing that removes spatial information a ``dislocator'' is still reasonable.
 
-Some ``dislocator'' functions we tried are
+Other ``dislocator'' functions whose output somehow describe the 
+distribution of features in their input should then work as substitutes
+for computing Gram matrices.
+The first few simplistic ``dislocator'' functions we tried are listed here.
+\begin{enumerate}
+\item Scaled sum of the responses all over the place for each feature.
+That is, for an $1\times64\times256\times256$ feature map,
+we compute an $1\times64$ array where each element is the sum of the
+$256\times256$ elements from the input.
+The whole array is then scaled to one over the total number of elements of the input feature map.
+\item Scaled sum of element-wise squares of the responses over the place for each feature.
+Other than an additional element-wise squaring, it is identical to the previous one.
+\item Scaled sum of absolute values of the responses over the place for each feature.
+\end{enumerate}
 

### 2019-05-27 rollback/neural-style.py
1

@@ -553,17 +553,36 @@ if False:
 cl = content_layers_default
 sl = style_layers_default
 (fname,f) = usableDislocators[0]
-for content_name,style_name in [('riverside','starrynight')]:
-		content_img = image_loader("./"+content_name+".jpg")
-		style_img = image_loader("./"+style_name+".jpg")
-		print(style_img.size(), content_img.size())
-		assert style_img.size() == content_img.size()
-		input_img = content_img.clone()
-		output = run_style_transfer(content_name+'-'+ style_name+'-'+str(imsize)+'-'+fname, 
+
+def one_experiment(): #relies on dynamic scoping!
+	content_img = image_loader("./"+content_name+".jpg")
+	style_img = image_loader("./"+style_name+".jpg")
+	print(style_img.size(), content_img.size())
+	assert style_img.size() == content_img.size()
+	input_img = content_img.clone()
+	output = run_style_transfer(content_name+'-'+ style_name+'-'+str(imsize)+'-'+fname, 
 									f, 
 									cl, sl,
 									cnn, cnn_normalization_mean, cnn_normalization_std,
 											content_img, style_img, input_img)
+
+
+for content_name in ['dancing','riverside']:
+	for style_name in ['picasso','starrynight']:
+		one_experiment()
+	
+if False:
+	for content_name,style_name in [('riverside','starrynight')]:
+			content_img = image_loader("./"+content_name+".jpg")
+			style_img = image_loader("./"+style_name+".jpg")
+			print(style_img.size(), content_img.size())
+			assert style_img.size() == content_img.size()
+			input_img = content_img.clone()
+			output = run_style_transfer(content_name+'-'+ style_name+'-'+str(imsize)+'-'+fname, 
+										f, 
+										cl, sl,
+										cnn, cnn_normalization_mean, cnn_normalization_std,
+												content_img, style_img, input_img)
 	
 
 

### 2019-05-27 rollback/neural-style.py
1

@@ -61,7 +61,7 @@ import torchvision.transforms as transforms
 import torchvision.models as models
 
 import copy
-
+import sys
 
 ######################################################################
 # Next, we need to choose which device to run the network on and import the
@@ -102,6 +102,9 @@ device = torch.device("cuda" if torch.cuda.is_available() else "cpu")
 #imsize = 32
 #imsize = 128
 imsize = 512
+
+if sys.argv[1] == "--one" and len(sys.argv) >= 5:
+	imsize = int(sys.argv[4])
 
 loader = transforms.Compose([
 	transforms.Resize(imsize),  # scale imported image
@@ -566,25 +569,19 @@ def one_experiment(): #relies on dynamic scoping!
 									cnn, cnn_normalization_mean, cnn_normalization_std,
 											content_img, style_img, input_img)
 
-
-for content_name in ['dancing','riverside']:
-	for style_name in ['picasso','starrynight']:
-		one_experiment()
+if False:
+	for content_name in ['dancing','riverside']:
+		for style_name in ['picasso','starrynight']:
+			one_experiment()
 	
 if False:
 	for content_name,style_name in [('riverside','starrynight')]:
-			content_img = image_loader("./"+content_name+".jpg")
-			style_img = image_loader("./"+style_name+".jpg")
-			print(style_img.size(), content_img.size())
-			assert style_img.size() == content_img.size()
-			input_img = content_img.clone()
-			output = run_style_transfer(content_name+'-'+ style_name+'-'+str(imsize)+'-'+fname, 
-										f, 
-										cl, sl,
-										cnn, cnn_normalization_mean, cnn_normalization_std,
-												content_img, style_img, input_img)
+		one_experiment()
 	
-
+if sys.argv[1] == "--one":
+	content_name = sys.argv[2]
+	style_name = sys.argv[3]
+	one_experiment()
 
 #plt.figure()
 #imshow(output, title='Output Image')

### 2019-05-27 paper/paper.tex
1

@@
 For example, minimising the mean square errors between two Gram matrices could be seen as 
-a special case for minimising a Maximum Mean Discrepancy, which means other Maximum Mean Discrepacies
+a special case for minimising a Maximum Mean Discrepancy (MMD), which means other Maximum Mean Discrepacies
 could be used \cite{MMD}.
+
+[[[[Maybe Describe MMD here]]]]
+
 For us, it seemed more natural to consider substitutes for the process itself of 
@@
 
+To find more dislocators, let us consider \emph{how to describe a distribution} in general?
+The obvious answer is then statistics, like mean, standard deviation,
+
 \section{Experiments and Discussion}
+
+\subsection{Reproducing the original result}
 

### 2019-05-27 paper/paper.tex
1

@@
 To find more dislocators, let us consider \emph{how to describe a distribution} in general?
-The obvious answer is then statistics, like mean, standard deviation,
+The obvious answer is then sample statistics or estimators, like (sample) mean, (sample) standard deviation, 
+(sample) skewness, (sample) kurtosis and any moments.
+Unfortunately, we found that higher moments are too slow to compute for experiments,
+so we ended up with the following (combinations) of sample statistics.
+%\begin{enumerate}
+%\end{enumerate}
 

### 2019-05-27 rollback/neural-style.py
Update neural-style.py

@@ -582,6 +582,8 @@ if sys.argv[1] == "--one":
 	content_name = sys.argv[2]
 	style_name = sys.argv[3]
 	one_experiment()
+else:
+    print("See readme.txt for instructions")
 
 #plt.figure()
 #imshow(output, title='Output Image')

### 2019-05-27 rollback/neural-style.py
Update neural-style.py

@@ -7,6 +7,8 @@ Neural Transfer Using PyTorch
  
 **Edited by**: `Winston Herring <https://github.com/winston6>`_
 
+**Edited by**: `Xi Du`
+
 Introduction
 ------------
 
@@ -71,7 +73,9 @@ import sys
 # Next, we set the ``torch.device`` for use throughout the tutorial. Also the ``.to(device)``
 # method is used to move tensors or modules to a desired device. 
 
-device = torch.device("cuda" if torch.cuda.is_available() else "cpu")
+device_str = "cuda" if torch.cuda.is_available() else "cpu"
+print('device is', device_str)
+device = torch.device(device_str)
 
 ######################################################################
 # Loading the Images

### 2019-05-27 rollback/neural-style.py
Update neural-style.py

@@ -73,7 +73,7 @@ import sys
 # Next, we set the ``torch.device`` for use throughout the tutorial. Also the ``.to(device)``
 # method is used to move tensors or modules to a desired device. 
 
-device_str = "cuda" if torch.cuda.is_available() else "cpu"
+device_str = "cpu"
 print('device is', device_str)
 device = torch.device(device_str)
 

### 2019-05-27 rollback/neural-style.py
Update neural-style.py

@@ -66,12 +66,7 @@ import copy
 import sys
 
 ######################################################################
-# Next, we need to choose which device to run the network on and import the
-# content and style images. Running the neural transfer algorithm on large
-# images takes longer and will go much faster when running on a GPU. We can
-# use ``torch.cuda.is_available()`` to detect if there is a GPU available.
-# Next, we set the ``torch.device`` for use throughout the tutorial. Also the ``.to(device)``
-# method is used to move tensors or modules to a desired device. 
+#GPU support is disabled because of lack of environments.
 
 device_str = "cpu"
 print('device is', device_str)

### 2019-06-01 paper/paper.tex
1

@@
 (sample) skewness, (sample) kurtosis and any moments.
-Unfortunately, we found that higher moments are too slow to compute for experiments,
+Unfortunately, we found that higher moments too slow to compute for our experiments,
 so we ended up with the following (combinations) of sample statistics.
-%\begin{enumerate}
-%\end{enumerate}
+\begin{enumerate}
+\item Mean and standard deviation of each type of feature. 
+That is, given a $1\times64\times256\times256$ feature map, 
+we compute an $1\times64\times2$ array.
+Standard deviation is favored over variance because standard deviations 
+are supposedly of the same unit of measure as the mean, 
+while variances are of a squared unit of measure.
+\item Mean, standard deviation and 4th central moment to the power of $1/4$. 
+That is, a $1\times64\times3$ array for a $1\times64\times256\times256$ feature map.
+\item Mean, standard deviation, 4th central moment to the power of $1/4$, 
+and 6th central moment to the power of $1/6$.
+\end{enumerate}
+We have found by experiment that odd-order moments did not work.
+6th central moments were already much slower to compute in practice 
+than Gram matrices.
+So we could only stop at the 6th moment due to limited experimental capacity.
+
+Unfortunately, straight forward histograms were not computationally feasible.
+Although the autograd facility could handle histograms in theory, we were not
+able to make histograms work in practice. Similarly, sorting or order statistics
+like medians were found to be computationally infeasible in practice.
 
@@
 \subsection{Reproducing the original result}
+[[[[Fill the experiment part in demo here to show that we have reproduced result.
+Cite the original tutorial]]]] \cite{tut}
+
+\subsection{Varying the extraction points for losses}
+
+We will now show that within the general optimisation framework,
+steps other than the Gram matrix, 
+such as the outputs of which feature maps to derive the style 
+losses from are not very essential.
 
@@
 
-\subsection{Varying the extraction points for losses}
-
-We will also show that other factors, such that the outputs of which functions to derive the style 
-losses from are not very essential and somewhat belongs to tuning.
+Now let us see something more interesting.
 
@@
 Paszke, A., Gross, S., Chintala, S., Chanan, G., Yang, E., DeVito, Z., Lin, Z., Desmaison, A., Antiga, L., \& Lerer, A. (2017). Automatic differentiation in PyTorch.
+\bibitem{tut}
+Jacq, A. (n.d.). Neural Transfer Using PyTorch (W. Herring, Ed.). Retrieved from https://pytorch.org/tutorials/advanced/neural\_style\_tutorial.html
 \end{thebibliography}

### 2019-06-01 rollback/neural-style.py

@@ -247,6 +247,7 @@ def dislocate8(arr):
 	return r
 
 usableDislocators = [
+	('identity',lambda x:x/x.shape.numel()),
 	('gram',gram_matrix),
 	('gram-n',gram_matrix_no_norm),
 	('sum',dislocate1),

### 2019-06-04 paper/paper.tex
Update on introduction by Jianzhen

@@
 
-\section{Literature Review}
+Image stylization is the process that mimics the appeal of artistic media [1] and converts input images into a stylized version.
+It is a research started with semi-automatic painting systems since 1990s [2] and can be used in many newly developed applications in machine learning and artificial intelligence [3].
+This technique leads to a new form of communication [4].
+With the use of image stylization, the media users can keep stylistic consistency on media platforms like Instagram or Twitter without obtaining skills in traditional artistic techniques [5].
+Image stylization allows users to generate picture in traditional artistic styles, which had been expensive and time-consuming with traditional techniques [19].
+It shifts the way how the media users share pictures on internet.
+At the beginning of the image stylization, which it started in 1980s, procedural filters and patch-based algorithms were studied and applied [4].
+One example for the procedural filters is to refine image with strokes placement algorithms, which a grid of rendering brush strokes is placed over an image [12, 13].
+Later on, patch-based synthesis was studied based on texture recognition [14].
+Moreover, these two methods have numerous difficulties in further developments on the capture of complex nuances of an artist’s style, and can only work for certain types of images [4].
+However, deep neural networks, which are developed as a general-purpose tool working different computer vision problems [15].
+The paper published by Leon Gatys in 2015 has proven that a simple neural network works well on the texture recognition just like the patch-based synthesis algorithms [16].
+One of the applications is auto-painter for cartoon image generation and it applies deep neural networks on image stylization [7].
+These computational bio-inspired neural networks mimic the basic structure of brain neurons.
+Like the auto-painter, convolutional neural network is used in this paper for developing a tool in image stylization.
+Neural networks, especially for the deep artificial neural networks, has been widely studied and used in the pattern recognition and machine learning in recent years [8].
+Convolutional neural network is one of the deep learning neural networks and have substantially achieved the state-of-the-art accuracies of object recognition [11].
+This is the key in image stylization where the essential features in the style image are extracted and applied on the input image.
+This paper applies a pre-trained CNN, VGG-19, on image stylization and extends its possibilities on image stylization.
+CNNs have a similar structure as ordinary neural networks, which include neurons with learnable weights and biases.
+CNNs are typically feed-forward architecture and widely used in computer vision tasks in recent years [11].
+Its basic unit is single neuron.
+Each of these neurons takes one or multiple inputs, conducts a dot product then optimally follows it with a non-linearity [9].
+The core mathematical equation for CNN is a result derived from two functions by integration and this indicates how one’s shape is changed by the other.
+CNN works in a way similar to broad categorization [10].
+When a CNN is used in image processing, every pixel of the input image will be processed by a feature detector and a feature map is given as the result.
+There will be very less, but critical features kept in the feature map compared to the input image.
+Consequently, some key features might be missed, and massive trainings are required for CNN’s accuracy on texture capture.
+
+\section{Related Work}
 

### 2019-06-04 paper/paper.tex
Updates on introduction and related work by Jianzhen

--- 2019-06-01 paper/paper.tex
@@
 
-\section{Literature Review}
+Image stylization is the process that mimics the appeal of artistic media [8] 
+and converts input images into a stylized version. It is a research started with
+semi-automatic painting systems since 1990s [1] and can be used in many newly 
+developed applications in machine learning and artificial intelligence [5]. 
+This technique leads to a new form of communication [2]. With the use of image 
+stylization, the media users can keep stylistic consistency on media platforms 
+like Instagram or Twitter without obtaining skills in traditional artistic 
+techniques [16]. Image stylization allows users to generate picture in 
+traditional artistic styles, which had been expensive and time-consuming with 
+traditional techniques [19]. It shifts the way how the media users share 
+pictures on internet. At the beginning of the image stylization, which it 
+started in 1980s, procedural filters and patch-based algorithms were studied 
+and applied [2]. One example for the procedural filters is to refine image 
+with strokes placement algorithms, which a grid of rendering brush strokes is 
+placed over an image [13, 3]. Later on, patch-based synthesis was studied based 
+on texture recognition [4]. Moreover, these two methods have numerous 
+difficulties in further developments on the capture of complex nuances of an 
+artist’s style, and can only work for certain types of images [2]. However, 
+deep neural networks, which are developed as a general-purpose tool working 
+different computer vision problems [5].  The paper published by Leon Gatys in 
+2015 has proven that a simple neural network works well on the texture 
+recognition just like the patch-based synthesis algorithms [14]. 
+One of the applications is auto-painter for cartoon image generation and it 
+applies deep neural networks on image stylization [11]. These computational 
+bio-inspired neural networks mimic the basic structure of brain neurons. 
+Like the auto-painter, convolutional neural network is used in this paper 
+for developing a tool in image stylization. Neural networks, especially for 
+the deep artificial neural networks, has been widely studied and used in the 
+pattern recognition and machine learning in recent years [17]. Convolutional 
+neural network is one of the deep learning neural networks and have 
+substantially achieved the state-of-the-art accuracies of object recognition 
+[12]. This is the key in image stylization where the essential features in the 
+style image are extracted and applied on the input image.
+
+This paper applies a pre-trained CNN, VGG-19, on image stylization and 
+extends its possibilities on image stylization. CNNs have a similar structure 
+as ordinary neural networks, which include neurons with learnable weights and 
+biases. CNNs are typically feed-forward architecture and widely used in computer
+vision tasks in recent years [12]. Its basic unit is single neuron. Each of 
+these neurons takes one or multiple inputs, conducts a dot product then 
+optimally follows it with a non-linearity [9]. The core mathematical equation 
+for CNN is a result derived from two functions by integration and this indicates 
+how one’s shape is changed by the other. CNN works in a way similar to broad 
+categorization [19]. When a CNN is used in image processing, every pixel of the 
+input image will be processed by a feature detector and a feature map is given 
+as the result. There will be very less, but critical features kept in the 
+feature map compared to the input image. Consequently, some key features might 
+be missed, and massive trainings are required for CNN’s accuracy on texture 
+capture.
+
+\section{Related Work}
+
+In the field of image stylization, there are abundant related work found.
+
+2.1 Image stylization using stroke-based and example-based methods
+
+Both stroke-based and example-based methods have been studied since last century 
+for image stylization. For the stroke-based stylization, one typical method is 
+that brush strokes are aligned based on input image for varying color, size and 
+orientation [18]. Many methods, which are developed based on brush strokes, 
+normally either focus on one specific type of brush or provides a generic 
+framework [7]. For an instance, a brush stroke for a traditional Japanese 
+sumi-e style painting creation is modelled with the use of a 1D array of 
+bristles and this method can only generate a stylized image in grey scale [20]. 
+One major disadvantage of the stroke-based method is that it cannot generate 
+result automatically and provides tools to users as they can tweak the output 
+[7]. Many researches have also pointed out that the complex nuances of an 
+artist’s style are too hard to be captured in some degrees [2]. As for the 
+example-based methods, texture recognition and transfer are the core parts [18].
+One framework for this method is called the image analogies, which is a basic 
+reasoning process and consisted of two stages: a design phase with training 
+data and application phase with new images [6]. This method is still being 
+studied but is more complex than the neural network [2].
+
+2.2 Image stylization using convolutional neural networks
+
+An extension to the example-based method would be the texture synthesis using 
+convolutional neural networks developed by Leon Gatys [14]. This is the 
+pre-trained CNN used in the paper, which is also known as VGG-19. Gram matrices 
+are introduced on the feature maps to transfer the representations into a 
+stationary feature space [14]. There are also other works that have used 
+convolutional neural networks for image stylization [10, 15]. In the process of 
+image stylization, there is a trade-off between content and style matching, 
+which is the content loss [10]. Furthermore, there are some limitations of 
+using VGG networks due to the zero-padding used for convolutions in VGG network 
+[14]. Overall, convolutional neural networks have a better performance than 
+previous works on image stylization [21].
+
+References for intro and related work:
+[1] Haeberli, P. (1990). Paint by numbers: abstract image representations. SIGGRAPH Comput Graph, 24 (4), pp. 207-214. doi: 10.1145/97880.97902
+[2] Hertzmann, A. (2018). Image Stylization: History and Future (Part1). Adobe Research. Viewed at: https://research.adobe.com/news/image-stylization-history-and-future/
+[3] Hertzmann, A.
+(1998).
+Painterly rendering with curved brush strokes of multiple sizes.
+Proceedings of the 25th annual conference on Computer graphics and interactive techniques, pp.
+453-460.
+doi: 10.1145/280814.280951
+[4] Hertzmann, A. (2018). Image Stylization: History and Future (Part2). Adobe Research. Viewed at: https://research.adobe.com/news/image-stylization-history-and-future-part-2/
+[5] Hertzmann, A. (2018). Image Stylization: History and Future (Part3). Adobe Research. Viewed at: https://research.adobe.com/news/image-stylization-history-and-future-part-3/
+[6] Hertzmann, A., Jacobs, C.
+E., Oliver, N., Curless, B., Salesin, D.
+H.
+(2001).
+Image analogies.
+Proceedings of the 28th annual conference on Computer graphics and interactive techniques, pp.
+327-340.
+doi: 10.1145/383259.383295
+[7] Hegde, S., Gatzidis, C., Tian, F. (2012). Painterly rendering techniques: a state‐of‐the‐art review of current approaches. Wiley Online Library. doi: 10.1002/cav.1435
+[8] Kyprianidis, J.E., Collomosse, J., Wang, T., Isenberg, T.
+(2013).
+State of the art: a taxonomy of artistic stylization techniques for images and video.
+IEEE Trans Vis Comput Graphics, 19 (5), pp.
+866-885.
+doi: 10.1109/TVCG.2012.160
+[9] Karpathy, A.
+(2019).
+Convolutional Neural Networks (CNNs/ConvNets).
+Stanford, CS231n Convolutional Neural Networks for Visual Recognition.
+Viewed at:  http://cs231n.github.io/convolutional-networks/
+[10] Krizhevsky, A., Sutskever, I., Hinton, G.
+E.
+(2012).
+ImageNet Classification with Deep Convolutional Neural Networks.
+NIPS proceedings.
+Viewed at: http://papers.nips.cc/paper/4824-imagenet-classification-with-deep-convolutional-neural-networ
+[11] Liu, Y., Qin, Z., Wan, T., Luo, Z.
+(2018).
+Auto-painter: Cartoon image generation from sketch by using conditional Wasserstein generative adversarial networks.
+Neurocomputing, Volume 311, pp.
+78-87.
+ISSN 0925-2312.
+doi: 10.1016/j.neucom.2018.05.045.
+[12] Liang, M., Hu, X.
+(2015).
+Recurrent Convolutional Neural Network for Object Recognition.
+IEEE Conference on Computer Vision and Pattern Recognition (CVPR), pp.
+3367-3375.
+Viewed at: http://openaccess.thecvf.com/content_cvpr_2015/html/Liang_Recurrent_Convolutional_Neural_2015_CVPR_paper.html
+[13] Litwinowicz, P. (1997). Processing images and video for an impressionist effect. Apple Computer, Inc., CA, DOI: 10.1145/258734.258893
+[14] Gatys, L.
+A., Ecker, A.
+S., Bethge, M.
+(2015), Texture Synthesis using Convolutional Neural Networks.
+Advances in Neural Information Processing Sytems 28 (NIPS 2015), Viewed at: http://papers.nips.cc/paper/5633-texture-synthesis-using-convolutional-neural-networks
+[15] Gatys, L.
+A., Ecker, A.
+S., Bethge, M.
+(2016).
+Image Style Transfer Using Convolutional Neural Networks.
+IEEE Conference on Computer Vision and Pattern Recognition (CVPR), pp.
+2414-2423.
+Viewed at: https://www.cv-foundation.org/openaccess/content_cvpr_2016/html/Gatys_Image_Style_Transfer_CVPR_2016_paper.html
+[16] Rosin, P., Collomosse, J. (2013). Image and Video-Based Artistic Stylisation. Springer. doi: 10.1007/978-1-4471-4519-6 
+[17] Schmidhuber, J. (2014). Deep learning in neural networks: An overview. Neural Networks, Volume 61, pp. 85-117. ISSN 0893-6080. doi: 10.1016/j.neunet.2014.09.003.
+[18] Semmo, A., Limberger, D., Kyprianidis, J.
+E., Döllner, J.
+(2016).
+Image stylization by interactive oil paint filtering.
+Computers & Graphics, Volume 55, pp.
+157-171, ISSN 0097-8493, doi: 10.1016/j.cag.2015.12.001.
+[19] Super Data Science (2018).
+Convolutional Neural Networks (CNN): Step 1 – Convolution Operation.
+Super Data Science.
+Viewed at: https://www.superdatascience.com/blogs/convolutional-neural-networks-cnn-step-1-convolution-operation/
+[20] Strassmann, S. (1986). Hairy brushes. Proceedings of the 13th Annual Conference on Computer Graphics and Interactive Techniques 1986, 20(4), pp.225–232.
+[21] Zhu, F., Yu, Y. (2018). Automatic Image Stylization using Deep Fully Convolutional Networks. The University of Hong Kong. Viewed at: https://arxiv.org/pdf/1811.10872.pdf
 

### 2019-06-04 paper/paper.tex
adding the conclusion & related items & inner para contents

--- 2019-06-01 paper/paper.tex
@@
 to half or even $\frac{1}{4}$ of the sizes of the image. 
-
 The functions $F_1,F_2,F_3,...$ now have meaningful names such as relu\_1, conv\_2 now.
-[[[[Not actually necessary to know but insert your elaborations here]]]]
 
@@
 The interative solver can be many, but in our case it is 
-L-BFGS [[[[Maybe elaborate on L-BFGS here]]]]. 
+L-BFGS.It is an optimisation methodology that approximates the BFGS (Broyden - 
+Fletcher - Goldfarb - Shanno) algorithm using optimal amount of system 
+memory. This algorithm is famous for estimating the parameters in Machine 
+Learning domain occupying only linear space for performing the computation. 
+The main goal of L-BFGS is to minimize the differentiable scalar function f(x)
+over the non-constrained values of  a real valued vector (x).
+
 The initial value of the argument could be either white noise or the content image,
@@
 \subsection{Gram matrix}
-[[[[Elaborate on gram matrix here]]]]
+Gram matrix is responsible for extracting the style of an image by specifically computing the style loss 
+from the style image. For Gram matrix computation, feature vectors are flattened for efficient computation 
+that could be easily explained with the help of dot products where more similar the vectors are, lesser the 
+angle of difference between them indicating the closer feature relation between image vectors. More angle of 
+difference indicates the varied feature image vectors.By computing the dot product of all convolutional 
+feature maps with every other feature map yields Gram Matrix which is formulated as,
 
@@
 could be used \cite{MMD}.
+Maximum Mean Discrepancy is the spatial probability measure distance that has enormous applications in 
+non-parametric testing and machine learning domain. It is defined as the distance between the neighbouring 
+mean elements in probability space.
 
-[[[[Maybe Describe MMD here]]]]
+MMDk(P, Q)=||μP * μQ||H Where μ is  the mean in the probability measure space.
 
@@
 (sample) skewness, (sample) kurtosis and any moments.
-Unfortunately, we found that higher moments too slow to compute for our experiments,
+Unfortunately, we found that higher moments are too slow to compute for experiments,
 so we ended up with the following (combinations) of sample statistics.
-\begin{enumerate}
-\item Mean and standard deviation of each type of feature. 
-That is, given a $1\times64\times256\times256$ feature map, 
-we compute an $1\times64\times2$ array.
-Standard deviation is favored over variance because standard deviations 
-are supposedly of the same unit of measure as the mean, 
-while variances are of a squared unit of measure.
-\item Mean, standard deviation and 4th central moment to the power of $1/4$. 
-That is, a $1\times64\times3$ array for a $1\times64\times256\times256$ feature map.
-\item Mean, standard deviation, 4th central moment to the power of $1/4$, 
-and 6th central moment to the power of $1/6$.
-\end{enumerate}
-We have found by experiment that odd-order moments did not work.
-6th central moments were already much slower to compute in practice 
-than Gram matrices.
-So we could only stop at the 6th moment due to limited experimental capacity.
-
-Unfortunately, straight forward histograms were not computationally feasible.
-Although the autograd facility could handle histograms in theory, we were not
-able to make histograms work in practice. Similarly, sorting or order statistics
-like medians were found to be computationally infeasible in practice.
+%\begin{enumerate}
+%\end{enumerate}
 
@@
 \subsection{Reproducing the original result}
-[[[[Fill the experiment part in demo here to show that we have reproduced result.
-Cite the original tutorial]]]] \cite{tut}
+
+\subsection{Varying the dislocator function}
 
@@
 
-We will now show that within the general optimisation framework,
-steps other than the Gram matrix, 
-such as the outputs of which feature maps to derive the style 
-losses from are not very essential.
+We will also show that other factors, such that the outputs of which functions to derive the style 
+losses from are not very essential and somewhat belongs to tuning.
 
-\subsection{Varying the dislocator function}
+\section{Conclusion}
+We have successfully implemented neural style transfer and generated the blende pastiche image
+using content image and style image. We have finally concluded that Artistic image is created
+with the help of pre-trained CNN. we did use vgg-19 model which is pre-trained model for object 
+and face detection and we saw how effectively it was able to detect the texture,and contour of
+the image. We determine the content loss by selecting a particular hidden layer’s activation. 
+We also determined the style loss with help of Gram Matrix of the hidden layer’s activations.
+Total style loss was computed by summing up all the style loss till the layers from where the
+content image is selected. Losses were evaluated by using gradient loss dynamically. This was
+computed using optimization algorithm of Broyden–Fletcher–Goldfarb–Shanno. This was done by 
+inputting the every iteration loss to the network.
 
-Now let us see something more interesting.
+\section{Observation}
+We found out that we can modify how much style of style image can be inserted in the final image. 
+In order to do this, we determined how much content and style of the content image and style image
+need to be present. These can be used as hyper parameters to develop the final artistic image. 
+More weights of the style of the style image leads to more style and content of the style image
+are going to be present in the generated image vice-versa. Another hyper parameter is to choose
+the CNN hidden layer activation for the content image. This helps to decide how much content
+of content images needs to present in the generated image.
 
-\section{Conclusion and Future Work}
+\section{Discussion}
+We did find that by putting more weights to style image, more style and content of style images
+were getting displayed. By putting in the context, when weights are 105  then content and style
+of the content image is lost and style of style image is on the generated image but content of
+style image was distorted. In the another process, we did choose different hidden activation layer
+in CNN for content image. Ideally, we have selected the middle layer which is ‘CONV_4’. We can
+select any of convolution layer to see different result. We found out that by selecting the CONV_1,
+the textures of the content image are more prominent. We also found it amazing that after the certain
+number of iterations, we are getting blacked out image. It could be possible that losses would have
+become zero in this case which further altering the pixel values of the image. However, this is 
+something need to be researched Thoroughly.
+
+\section{Lessons Learnt}
+We were able to use Pytorch and Tensorflow libraries to implement the image stylization.
+We also understood how well CNN model works when image is given as input. We learned to 
+compute difference between the two images with the help of content and style. This can be 
+computed with the help of gradient loss.
+
+\section {Future Work}
+At present, we are applying style of the style image to the whole content image. We are thinking
+of using image segmentation technique[1] so to apply style on a particular segment of the image. 
+For example, there is a photograph of person wearing a jacket, applying this new technique, 
+we would style the jacket with help of some art and apply it back to original image. This means 
+old jacket becomes the new one.
+
+\section{Summary of Learning Outcome} 
+We learned some crucial concept of programming the project in python using pyTorch and Tensorflow. 
+We analysed and evaluated neural style transfer algorithm. We also learned to examined the research
+paper and how to link the research paper with other researches to form an innovation solutions. 
+We also learned to work in a team. We were able to reflect and use the course learning as our future
+work for the neural style transfer.
 
@@
 Paszke, A., Gross, S., Chintala, S., Chanan, G., Yang, E., DeVito, Z., Lin, Z., Desmaison, A., Antiga, L., \& Lerer, A. (2017). Automatic differentiation in PyTorch.
-\bibitem{tut}
-Jacq, A. (n.d.). Neural Transfer Using PyTorch (W. Herring, Ed.). Retrieved from https://pytorch.org/tutorials/advanced/neural\_style\_tutorial.html
 \end{thebibliography}

### 2019-06-04 paper/paper.tex

--- 2019-06-04 paper/paper.tex
@@
 
-\section{Conclusion and Future Work}
+\section{Conclusion}
+We have successfully implemented neural style transfer and generated the blende pastiche image
+using content image and style image. We have finally concluded that Artistic image is created
+with the help of pre-trained CNN. we did use vgg-19 model which is pre-trained model for object 
+and face detection and we saw how effectively it was able to detect the texture,and contour of
+the image. We determine the content loss by selecting a particular hidden layer’s activation. 
+We also determined the style loss with help of Gram Matrix of the hidden layer’s activations.
+Total style loss was computed by summing up all the style loss till the layers from where the
+content image is selected. Losses were evaluated by using gradient loss dynamically. This was
+computed using optimization algorithm of Broyden–Fletcher–Goldfarb–Shanno. This was done by 
+inputting the every iteration loss to the network.
+
+\section{Observation}
+We found out that we can modify how much style of style image can be inserted in the final image. 
+In order to do this, we determined how much content and style of the content image and style image
+need to be present. These can be used as hyper parameters to develop the final artistic image. 
+More weights of the style of the style image leads to more style and content of the style image
+are going to be present in the generated image vice-versa. Another hyper parameter is to choose
+the CNN hidden layer activation for the content image. This helps to decide how much content
+of content images needs to present in the generated image.
+
+\section{Discussion}
+We did find that by putting more weights to style image, more style and content of style images
+were getting displayed. By putting in the context, when weights are 105  then content and style
+of the content image is lost and style of style image is on the generated image but content of
+style image was distorted. In the another process, we did choose different hidden activation layer
+in CNN for content image. Ideally, we have selected the middle layer which is ‘CONV_4’. We can
+select any of convolution layer to see different result. We found out that by selecting the CONV_1,
+the textures of the content image are more prominent. We also found it amazing that after the certain
+number of iterations, we are getting blacked out image. It could be possible that losses would have
+become zero in this case which further altering the pixel values of the image. However, this is 
+something need to be researched Thoroughly.
+
+\section{Lessons Learnt}
+We were able to use Pytorch and Tensorflow libraries to implement the image stylization.
+We also understood how well CNN model works when image is given as input. We learned to 
+compute difference between the two images with the help of content and style. This can be 
+computed with the help of gradient loss.
+
+\section {Future Work}
+At present, we are applying style of the style image to the whole content image. We are thinking
+of using image segmentation technique[1] so to apply style on a particular segment of the image. 
+For example, there is a photograph of person wearing a jacket, applying this new technique, 
+we would style the jacket with help of some art and apply it back to original image. This means 
+old jacket becomes the new one.
+
+\section{Summary of Learning Outcome} 
+We learned some crucial concept of programming the project in python using pyTorch and Tensorflow. 
+We analysed and evaluated neural style transfer algorithm. We also learned to examined the research
+paper and how to link the research paper with other researches to form an innovation solutions. 
+We also learned to work in a team. We were able to reflect and use the course learning as our future
+work for the neural style transfer.
 
